---
title: "Introduction to mhealthannotator"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{how_to_mhealthannotator}
  %\VignetteEngine{knitr::knitr}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Overview

mhealthannotator is used as a dashboard-as-a-service that can interact easily with Synapse through parsing File Attachments in Synapse Tables. It gives user the flexibility to parse config file and a custom visualization function to a given filepath.

## Installing 
```{r eval = FALSE}
devtools::install_github("Sage-Bionetworks/mhealthannotator")
```


## Load Library
```{r setup, warning = FALSE}
library(mhealthannotator)
```


## Mhealthannotator Usage

### 1. Create Visualization Function

To create a visualization function, expected input is any parse-able data json, jpeg etc. And output will a filepath to the processed files.

```{r eval=FALSE}
## a good and simple example is to make a function that takes in filepath
## and convert to jpeg if image is png format
visualize_photo <- function(filepath){
    if(tools::file_ext(filepath) == "png"){
        new_filepath <- sub('\\.png$', '.jpg', filepath)
        png_mat <- png::readPNG(filepath)
        jpeg::writeJPEG(png_mat, target = new_filepath, quality = 1)
        file.remove(filepath)
        return(new_filepath)
    }else{
        return(filepath)
    }
}
```

### 2. Create Configuration File

To create a config file, the app will accept .yml files containing key-values pair. You can refer to create_config vignette for more info on how to write the configurations file.

```{r eval=FALSE}
# template to use for config file
default:
    synapse_opts:
        output_parent_id: 
            - "syn25614357"
        synapse_tbl_id: 
            - "syn22281748" 
        output_filename: 
            - "psoriasis_plaque_annotations.tsv"
        filehandle_cols:
            - "psoriasisAreaPhoto.jpg"
            - "psoriasisAreaPhoto.png"
        uid: 
            - "recordId" # unique identifier for that file in synapse table
        n_batch: 5
        keep_metadata:
            - "participantId"
            - "createdOn"
        sort_keys:
            - "recordId" # optional
    survey_opts:
        survey_1:
                colname: "PGA"
                type: "radio"
                prompt: "PGA:"
                input_choices:
                    0: 0
                    1: 1
                    2: 2
                    3: 3
                    4: 4
                    Cannot Tell: "Cannot Tell"
        survey_2:
            colname: "erythema"
            type: "checkbox_group"
            prompt: "Erythema:"
            input_choices:
                0: 0
                1: 1
                2: 2
                3: 3
                4: 4
                Cannot Tell: "Cannot Tell"
        survey_3:
            colname: "induration"
            type: "slider"
            prompt: "Induration:"
            input_choices:
                min: 0
                max: 5
                step: 1
        survey_4:
            colname: "scaling"
            type: "slider"
            prompt: "Scaling:"
            input_choices:
                min: 0
                max: 5
                step: 1
    image_opts:
        width: "auto"
        height: "auto"
```


### 3. Run your App using the config and visualization function

To run the app, you will only require two parameters, which is the configurations file and your desired function. 

```{r eval=FALSE}
mhealthannotator::run_app(
    config = "/path/to/config/file",
    funs = visualize_photo
)
```

